### 2024-09-23 proposal-documents/white-paper/white-paper-phd-proposal.tex
white paper cleanup
new white paper

%%%%% toc and glossaries
\usepackage[toc,title]{appendix}
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries
\usepackage{titlesec,titletoc}
%\renewcommand{\thepart}{ARTICLE \Roman{part}} %puts the label into the command so \thelabel will carry through
%\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
\titleformat{\part}{\normalfont\large\bfseries}{\thepart}{}{}[]
\titlespacing*\part{0pt}{0.95\baselineskip}{0.75\baselineskip}
\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
\titlespacing*\section{0pt}{0.65\baselineskip}{0.55\baselineskip}
\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
\titlespacing*\subsection{0pt}{0.50\baselineskip}{0.35\baselineskip}
\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
\titlespacing*\paragraph{0pt}{0.45\baselineskip}{0.25\baselineskip}
\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
%\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
%\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
%\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
%\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
%%%%%

@@

%%%%% linenumbering
\linenumbers %toggle line numbers
\pagewiselinenumbers %reset line numbers on new page
\modulolinenumbers[1] %line numbering interval
%%%%%

@@

\part*{Abstract}

\section*{Overview}

\section*{Overall objective}

\section*{Motivation}
\subsection*{Context}

\section*{Novelty of the work}

\section*{Relevant literature}

\section*{Logical path to work accomplishment} 
\begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Workscope title} 
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{This task.}
            \item\textit{That task.}
            \item\textit{Another task.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item A brief explanation or a subtask if needed.
                \end{enumerate*}
        \end{enumerate}
\end{enumerate}

\paragraph*{Goals}
The goals of this Workscope are \ldots .

@@

\paragraph*{Goals}
The goals of this Workscope are \ldots .

@@

\paragraph*{Goals}
The goals of this Workscope are \ldots .

{\small
\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|}
%        \captionsetup{margin=-9pt}
        \caption*{\textbf{Timeframe for execution of proposed project.}}
        \label{tab-timeline}\\
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}&
        \multicolumn{5}{|c|}{\textbf{MONTH}}
        \\
        \cline{2-6}
        &
        \textbf{JAN}&
        \textbf{FEB}&
        \textbf{MAR}&
        \textbf{APR}&
        \textbf{MAY}
        \\
        \hline
        I.
        &\x
        &
        &
        &
        &
        \\
        \hline
        II.
        &\x
        &
        &
        &
        &
        \\
        \hline
        III.
        &\x
        &
        &
        &
        &
        \\
        \hline
        IV.
        &\x
        &
        &
        &
        &
        \\
        \hline
        V.
        &\x
        &
        &
        &
        &
        \\
        \hline
        VI.
        &\x
        &
        &
        &
        &
        \\
        \hline
        VII.
        &
        &
        &
        &
        &\x
        \\
        \hline
        XX. Lessons learned
        &
        &
        &
        &\x
        &\x
        \\
        \hline
        XX. Future work
        &
        &
        &
        &\x
        &\x
        \\
        \hline
        XX. Reprod. \& validation
        &
        &
        &
        &\x
        &\x
        \\
        \hline
\end{longtable}
}

@@

    \renewcommand{\thesection}{\Roman{section}}
    \titleformat{\section}{\normalfont\large\bfseries}{Appendix \thesection:}{1ex}{}[]

    \section*{Acronyms}
    \printnoidxglossary[title={}]

>>>>

%%%%% toc and glossaries
\usepackage[toc,title]{appendix}
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries
\usepackage{titlesec,titletoc}
%%%
\titleformat{\part}{\normalfont\normalsize\bfseries\filcenter}{\thepart}{}{}[]
\titlespacing*\part{0pt}{0.50\baselineskip}{0.25\baselineskip}

\titleformat{\section}[runin]{\normalfont\normalsize\bfseries}{\thesection.}{0.5em}{}[]
\titlespacing*\section{0pt}{0.50\baselineskip}{0.50\baselineskip}

\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesection\alph{subsection}.}{0.25em}{}[]
\titlespacing*\subsection{0pt}{0.40\baselineskip}{0.50\baselineskip}

\titleformat{\subsubsection}[runin]{\normalfont\normalsize\bfseries}{\roman{subsubsection}.}{0.25em}{}[]
\titlespacing*\subsubsection{9pt}{0.25\baselineskip}{0.50\baselineskip}

\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries}{\theparagraph}{-1em}{}[]
\titlespacing*\paragraph{0pt}{0.40\baselineskip}{0.50\baselineskip}

\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{0.25em}{}[]
\titlespacing*\subparagraph{15pt}{0.25\baselineskip}{0.50\baselineskip}
%%%
%\titleformat{\part}{\normalfont\large\bfseries\filcenter}{\thepart}{}{}[]
%\titlespacing*\part{0pt}{0.65\baselineskip}{0.20\baselineskip}
%\titleformat{\section}{\normalfont\normalsize\bfseries\filcenter}{\thesection}{}{}[]
%\titlespacing*\section{0pt}{0.50\baselineskip}{0.15\baselineskip}
%\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
%\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.25\baselineskip}
%\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
%\titlespacing*\paragraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
%\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
%\titlespacing*\subparagraph{0pt}{0.35\baselineskip}{0.25\baselineskip}
%%%
%\renewcommand{\thepart}{ARTICLE \Roman{part}} %puts the label into the command so \thelabel will carry through
%\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
%\titleformat{\part}{\normalfont\large\bfseries}{\thepart}{}{}[]
%\titlespacing*\part{0pt}{0.50\baselineskip}{0.75\baselineskip}
%\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[]
%\titleformat{\section}{\normalfont\large\bfseries\filcenter}{\thesection}{}{}[]
%\titlespacing*\section{0pt}{0.75\baselineskip}{0.45\baselineskip}
%\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
%\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.25\baselineskip}
%\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
%\titlespacing*\paragraph{0pt}{0.35\baselineskip}{0.15\baselineskip}
%\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
%\titlespacing*\subparagraph{0pt}{0.30\baselineskip}{0.10\baselineskip}
%\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
%\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
%\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
%\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
%%%%%

@@

%%%%% linenumbering
\linenumbers %toggle line numbers
\pagewiselinenumbers %reset line numbers on new page
\modulolinenumbers[5] %line numbering interval
%%%%%

@@

\part*{Overview}

\section{Proposed research}

\section{Overall objective}

\section{Motivation}
\subsection{Context}

\section{Novelty of the work}

\section{Relevant literature}

\section{Methodoloy}

\part*{Major Outcomes \& Deliverables}

\section{Preliminary results}

\section{Research scope} 
\begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Workscope title} 
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{This task.}
            \item\textit{That task.}
            \item\textit{Another task.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item A brief explanation or a subtask if needed.
                \end{enumerate*}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[series=milestone,topsep=0pt,itemsep=-0.5ex,partopsep=0ex,parsep=1ex,label=\textbf{\textit{Milestone \arabic*.}},align=left,leftmargin=*]
    \item\textit{.}
\end{enumerate}

@@

\begin{enumerate}[resume=milestone,topsep=0pt,itemsep=-0.5ex,partopsep=0ex,parsep=1ex,label=\textbf{\textit{Milestone \arabic*.}},align=left,leftmargin=*]
    \item\textit{.}
\end{enumerate}

@@

\begin{enumerate}[resume=milestone,topsep=0pt,itemsep=-0.5ex,partopsep=0ex,parsep=1ex,label=\textbf{\textit{Milestone \arabic*.}},align=left,leftmargin=*]
    \item\textit{.}
\end{enumerate}

\part*{\textbf{Timeframe for Execution}}
{\small
\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|}
%        \captionsetup{margin=-9pt}
        \caption*{}
        \label{tab-timeline}\\
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}&
        \multicolumn{5}{|c|}{\textbf{MONTH/YEAR}}
        \\
        \cline{2-6}
        &
        \textbf{JAN}&
        \textbf{FEB}&
        \textbf{MAR}&
        \textbf{APR}&
        \textbf{MAY}
        \\
        \hline
        I.
        &\x
        &
        &
        &
        &
        \\
        \hline
        II.
        &\x
        &
        &
        &
        &
        \\
        \hline
        III.
        &\x
        &
        &
        &
        &
        \\
        \hline
        IV.
        &\x
        &
        &
        &
        &
        \\
        \hline
        V.
        &\x
        &
        &
        &
        &
        \\
        \hline
        VI.
        &\x
        &
        &
        &
        &
        \\
        \hline
        VII.
        &
        &
        &
        &
        &\x
        \\
        \hline
        XX. Lessons learned
        &
        &
        &
        &\x
        &\x
        \\
        \hline
        XX. Future work
        &
        &
        &
        &\x
        &\x
        \\
        \hline
        XX. Reprod. \& validation
        &
        &
        &
        &\x
        &\x
        \\
        \hline
\end{longtable}
}

@@

    \renewcommand{\thesection}{\Roman{section}}
    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]

    \section{Acronyms}
    \printnoidxglossary[title={}]
